---
title: "Group3_Project"
author: "Bundi Kirimi"
date: "2/7/2022"
output: html_document
---





```{r}
#Loading the data
path <-"C:/Users/Jerome/Downloads/Daegu_Real_Estate_data.csv" 

df<-read.csv(path, sep = ",")

head(df)
```


#Previewing the summary of the dataset
```{r}
summary(df)
```

#Checking the data
```{r}
#Length
length(df)
```
The dataframe has 16 columns


````{r}
#Dimensions
dim(df)

````




#The dataframe has 12330 row entries and 18 columns
Column Names
```{r}
colnames(df)

```

Column data types

```{r}
sapply(df, class)
```




#Data Cleaning

```{r}

any(is.na(df))
```

```{r}
#Duplicates
duplicated_rows <- df[duplicated(df),]

dim(duplicated_rows)

```
Removing duplicates
```{r}
df1 <- df[-which(duplicated(df)), ]
dim(df1)
```

#Data Types
```{r}

sapply(df1, class)
```

```{r}
summary(df1)
```

median is 212,389..This will be the nedium priced house
32,743 will be the least price
585,840 the most expensive house

#Univariate Analysis

```{r}
factor(unique(df1$SalePrice))


````

```{r}
unique(df1$HallwayType)

factor(unique(df1$HallwayType))

```


```{r}
unique(df1$HeatingType)

factor(unique(df1$HeatingType))
```

```{r}
unique(df1$AptManageType)

factor(unique(df1$AptManageType))
```


```{r}
unique(df1$HallwayType)
factor(unique(df1$HallwayType))
````


```{r}
#HallwayTypecorridor                   HallwayTypemixed                HallwayTypeterraced
#each of the values printed below appear thrice in the dataset
#distribution
hist(df$YrSold , col=c("darkorange"))
````


```{r}
#HallwayTypecorridor                   HallwayTypemixed                HallwayTypeterraced
#each of the values printed below appear thrice in the dataset
#distribution
hist(df1$SalePrice , col=c("darkorange"))


`````
```{r}
#HallwayTypecorridor                   HallwayTypemixed                HallwayTypeterraced
#each of the values printed below appear thrice in the dataset
#distribution
hist(df1$YearBuilt , col=c("darkorange"))
````


```{r}
#HallwayTypecorridor                   HallwayTypemixed                HallwayTypeterraced
#each of the values printed below appear thrice in the dataset
#distribution
hist(df1$YrSold , col=c("darkorange"))
````

```{r}
#HallwayTypecorridor                   HallwayTypemixed                HallwayTypeterraced
#each of the values printed below appear thrice in the dataset
#distribution
hist(df1$MonthSold , col=c("darkorange"))
````

```{r}
#HallwayTypecorridor                   HallwayTypemixed                HallwayTypeterraced
#each of the values printed below appear thrice in the dataset
#distribution
hist(df1$Size.sqf. , col=c("darkorange"))
````

```{r}
#HallwayTypecorridor                   HallwayTypemixed                HallwayTypeterraced
#each of the values printed below appear thrice in the dataset
#distribution
hist(df1$Floor , col=c("darkorange"))
````











facto
Performing one hot encoding

```{r}
# One hot encoding of the factor variables.
library(caret)
## Loading required package: lattice
dmy <- dummyVars(" ~ .", data = df1)
dummy_df <- data.frame(predict(dmy, newdata = df1))

#print(dummy_df)
head(dummy_df)

```

Checking the datatypes

```{r}
sapply(dummy_df, class)

```







Regression




